$P$ versus $NP$

### 2020-02-10 doc/manuscript.tex
Finalized the whole proof

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We demonstrate if L is not equal to NL, then P = NP. In addition, we show if L is equal to NL, then P = NP. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class NL is equal to NP.
\end{abstract}

@@

\begin{theorem}
$NL = NP$.
\end{theorem}

@@

@@

We also prove that $NL = NP$. There are several important consequences from this result, but we will only mention one of the principal outcomes, that would be the application of Theorem Buhrman-Fortnow-van Melkebeek-Torenvliet when $NL = NP$ \cite{BU00}.

>>>>

%TODO mandatory: add short abstract of the document
\begin{abstract}
P versus NP is considered as one of the most important open problems in computer science. This consists in knowing the answer of the following question: Is P equal to NP? It was essentially mentioned in 1955 from a letter written by John Nash to the United States National Security Agency. However, a precise statement of the P versus NP problem was introduced independently by Stephen Cook and Leonid Levin. Since that date, all efforts to find a proof for this problem have failed. Another major complexity classes are L and NL. Whether L = NL is another fundamental question that it is as important as it is unresolved. We demonstrate if L is not equal to NL, then P = NP. In addition, we show if L is equal to NL, then P = NP. In this way, we prove the complexity class P is equal to NP. Furthermore, we demonstrate the complexity class L is equal to NP.
\end{abstract}

@@

\begin{theorem}
\label{nl}
$NL = NP$.
\end{theorem}

@@

\begin{theorem}
$L = NP$.
\end{theorem}

\begin{proof}
Under the assumption of $L \subseteq 1NL$, then we would obtain that $1NL = NL$. Certainly, the logarithmic space verifier of Theorem \ref{proof} works into one-way when $L \subseteq 1NL$. Indeed, the logarithmic space verifier through the certificate generates the output into one-way according to the arguments provided by the proof in Theorem \ref{proof}. Moreover, we know that $\textit{XOR 2SAT} \in 1NL$ under the assumption of $L \subseteq 1NL$, since $\textit{XOR 2SAT}$ is in $L$ \cite{AR00}, \cite{RM08}. In this way, we obtain that $MAX\oplus2SAT \in 1NL$. Since $MAX\oplus2SAT$ is $\textit{NP--complete}$ under logarithmic space reductions and $NL = NP$ due to Theorem \ref{nl}, then we would deduce that $1NL = NL$, because of every problem in $NP$ could be reduced to $MAX\oplus2SAT$ under $1NL$-reductions. However, it is a known result that $1NL \neq NL$ \cite{MI92}. Consequently, we obtain that $1NL \subset L$ as a consequence of this contradiction. Since $1NL \subset L$ implies $L=NL$ \cite{HM81}, then we have the complexity class $L$ is equal to $NP$.
\end{proof}

@@

### 2020-02-10 doc/presentation.tex
Finalized the whole proof

\begin{frame}{$NL$ versus $NP$}

\begin{theorem}
$NL = NP$.
\end{theorem}

@@

>>>>

\begin{frame}{Extended version: $NL$ versus $NP$}

\begin{theorem}
\label{nl}
$NL = NP$.
\end{theorem}

@@

\begin{frame}{Extended version: $L$ versus $NP$}

\begin{theorem}
$L = NP$.
\end{theorem}

Under the assumption of $L \subseteq 1NL$, then we would obtain that $1NL = NL$. Certainly, the logarithmic space verifier of Theorem \ref{proof} works into one-way when $L \subseteq 1NL$. Indeed, the logarithmic space verifier through the certificate generates the output into one-way according to the arguments provided by the proof in Theorem \ref{proof}. Moreover, we know that $\textit{XOR 2SAT} \in 1NL$ under the assumption of $L \subseteq 1NL$, since $\textit{XOR 2SAT}$ is in $L$. In this way, we obtain that $MAX\oplus2SAT \in 1NL$. 
\end{frame}

Since $MAX\oplus2SAT$ is $\textit{NP--complete}$ under logarithmic space reductions and $NL = NP$ due to Theorem \ref{nl}, then we would deduce that $1NL = NL$, because of every problem in $NP$ could be reduced to $MAX\oplus2SAT$ under $1NL$-reductions. However, it is a known result that $1NL \neq NL$. Consequently, we obtain that $1NL \subset L$ as a consequence of this contradiction. Since $1NL \subset L$ implies $L=NL$, then we have the complexity class $L$ is equal to $NP$. \qed
